Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-05 journal paper/content/related_work.tex
small fixes in related work

\asedit{\citet{keller2003price} studied the interplay of exploration and competition \emph{on prices}. This distinction leads to several important differences. First, the data externality -- that each customer brings a new data point to a given principal if and only if he chooses this principal -- is absolutely crucial to our setting, and absent in theirs. Second, the inputs to agents' decision rule are prices (which are directly controlled by the principals), rather than the quality of the chosen actions (which is not known a priori). Their focus on learning the decision rule, whereas ours is on learning quality. Third, they consider strategies that respond to competition and analyze Markov Perfect Equilibria, whereas we focus on adoption of better bandit algorithms.}

@@

\cite{schmalensee1982product, bagwell1990informational} investigate how buyer uncertainty about product quality can serve as a barrier to entry for late arrivers. We observe a similar effect when we investigate the role that reputation can serve as a barrier to entry. \asmargincomment{I can't parse this sentence, could you pls simplify?}
However, in our model this effect is further strengthened by the fact that the firms have to learn while competing adding that the incumbent may not only have a reputational advantage, but additionally has a further advantage due to the data it acquires in the incumbency period. Thus, our model also highlights the role that data can serve as a barrier to entry in online markets which has similarly been noted in \cite{de2020data}. For an extensive overview of the other channels through which first-mover advantages can lead to a competitive advantage, see \cite{kerin1992first}.

>>>>

\asedit{\citet{keller2003price} studied the interplay of exploration and competition \emph{on prices}. This distinction leads to several important differences. First, the data externality -- that each customer brings a new data point to a given principal if and only if he chooses this principal -- is absolutely crucial to our setting, and absent in theirs. Second, the inputs to agents' decision rule are prices (which are directly controlled by the principals), rather than the quality of the chosen actions (which is not known a priori). Their focus \gaedit{is} on learning the decision rule, whereas ours is on learning \gaedit{product} quality. Third, they consider strategies that respond to competition and analyze Markov Perfect Equilibria, whereas we focus on \gaedit{the} adoption of better bandit algorithms.}

@@

\cite{schmalensee1982product, bagwell1990informational} investigate how buyer uncertainty about product quality can serve as a barrier to entry for late arrivers. We observe a similar effect when we investigate the role that reputation can serve as a barrier to entry. \asmargincomment{I can't parse this sentence, could you pls simplify?}\gaedit{In our model the first-mover advantage further provides the incumbent with a ``head start" on data collection relative to the late arrivers.}
\gadelete{However, in our model this effect is further strengthened by the fact that the firms have to learn while competing adding that the incumbent may not only have a reputational advantage, but additionally has a further advantage due to the data it acquires in the incumbency period.}Thus, our model also highlights the role that data can serve as a barrier to entry in online markets which has similarly been noted in \cite{de2020data}. For an extensive overview of the other channels through which first-mover advantages can lead to a competitive advantage, see \cite{kerin1992first}.
